On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-07-03 article/msculled_revised_2.tex
points 2 and 3 adressed. relevent text henceforth: msculled_revised_2.tex]

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost data.}
    \label{KvsMg}
\end{figure}
 %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
    \label{KvsFe}
\end{figure}

Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. As described in Section \ref{sec:method}, we are forced to adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe] for our sample stars as we are unable to estimate [Mg/Fe] from the LAMOST spectra. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE and for over 60000 stars from APOGEE \citep{alam2015} is also shown. We note that [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population. The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundances in NGC 2808.

@@

\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{data:lamost}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
\end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015} as well as the three candidates observed using Magellan/MIKE (red diamonds). These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles). Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
    \label{KvsMg}
\end{figure}
 %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
    \label{KvsFe}
\end{figure}

Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. As described in Section \ref{sec:method}, we are forced to adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe] for our sample stars as we are unable to estimate [Mg/Fe] from the LAMOST spectra. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE and for over 60000 stars from APOGEE \citep{alam2015} is also shown. The \lamost\ abundances for the three stars observed by Magellan are also shown (red circles). We note that [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population. The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundances in NGC 2808.

@@

\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{data:lamost}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.2871 & 12.8061 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
J002619.36+565612.1 & 6.5807 & 56.9367 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
J002907.61+354701.0 & 7.2817 & 35.7836 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
J003451.10+424543.0 & 8.7130 & 42.7620 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
J005649.98+391722.9 & 14.2083 & 39.2897 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
J010305.95+043445.9 & 15.7748 & 4.5794 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
J011949.36+063411.4 & 19.9557 & 6.5699 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
J013039.08+404843.8 & 22.6628 & 40.8122 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
J030101.42+560042.3 & 45.2560 & 56.0118 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
J032423.46+425429.6 & 51.0978 & 42.9082 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
\end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
